Treatment heterogeneity in comparative effectiveness of teriparatide vs bisphosphonates: multi-database cohort study

### 2021-12-22 submission/manuscript.rmd
start table 1

@@

When using the internally developed hip fracture risk prediction models to divide the population into lower 75\% and top 25\% risk subgroups, we observed....

>>>>

```{r, echo=FALSE, warning=FALSE, message=FALSE}

ccae <- tibble(
  database = "ccae",
  variable = c(
    "Osteoarthritis",
    "Rheumatoid arthritis",
    "Renal impairment",
    "Crohn's disease",
    "Obesity",
    "Antithrombotic agents",
    "Drugs used in diabetes",
    "Lipid modifying agents",
    "Drugs for obstructive airway diseases",
    "Immunosuppressants",
    "Antineoplastic agents",
    "Antiinflammatory and antireumatic agents",
    "Opioids",
    "Antiepileptics",
    "Psycholeptics",
    "Antidepressants"
  ),
  treatment = c(
    41.7, 7.6, 4, 1.4, 4.8, 11.7, 7.2, 26.8, 44.3, 12.1,
    11.8, 36.8, 43.3, 23.7, 40.7, 39.2
  ),
  comparator = c(
    23.3, 4.1, 1.7, .7,
    2.9, 6, 6.3, 29.2,
    34.2, 6.2, 8.6, 28.4,
    26.8, 12, 28.3, 28.4
  ),
  std_difference = c(
    -.23, -.1, -.09, -.25,
    -.07, -.14, -.03, .03,
    -.11, -.14, -.07, -.1,
    -.2, -.2, -.15, -.13
  )
)

optum_ehr <- tibble(
  database = "optum-ehr",
  variable = c(
    "Osteoarthritis",
    "Rheumatoid arthritis",
    "Renal impairment",
    "Crohn's disease",
    "Obesity",
    "Antithrombotic agents",
    "Drugs used in diabetes",
    "Lipid modifying agents",
    "Drugs for obstructive airway diseases",
    "Immunosuppressants",
    "Antineoplastic agents",
    "Antiinflammatory and antireumatic agents",
    "Opioids",
    "Antiepileptics",
    "Psycholeptics",
    "Antidepressants"
  ),
  treatment = c(
    39.6, 7.7, 8.3,
    1, 5.9, 41.4, 11.3, 35.6,
    48.4, 11.7, 12, 55.7, 49.7,
    28, 44.3, 39.2 
  ),
  comparator = c(
    30.3, 4.7, 8.4, .6, 6.2,
    38.5, 12.4, 42.3, 42.2, 6.6,
    8.2, 50.5, 33.4, 17.3, 34.5, 31
  ),
  std_difference = c(
    -.11, -.09, 0, -.03, .01,
    -.03, .02, .08, -.07, -.12,
    -.09, -.05, -.18, -.16, -.11, -.1
  )
)

optum_dod <- tibble(
  database = "optum-dod",
  variable = c(
    "Osteoarthritis",
    "Rheumatoid arthritis",
    "Renal impairment",
    "Crohn's disease",
    "Obesity",
    "Antithrombotic agents",
    "Drugs used in diabetes",
    "Lipid modifying agents",
    "Drugs for obstructive airway diseases",
    "Immunosuppressants",
    "Antineoplastic agents",
    "Antiinflammatory and antireumatic agents",
    "Opioids",
    "Antiepileptics",
    "Psycholeptics",
    "Antidepressants"
  ),
  treatment = c(
    56.6, 10.3, 12.7, 1.1, 7.3,
    18.9, 11.1, 38.5, 48.1, 12.8,
    13.9, 37.3, 50.1, 27.2, 40.2, 41.1
  ),
  comparator = c(
    38.6, 5.3, 9.4, .5, 5.9,
    12.6, 11.8, 43.1, 37, 5.8,
    8.9, 28.2, 29.6, 15, 26.8, 29
  ),
  std_difference = c(
    -.18, -.13, -.07, -.04, -.04,
    -.11, .02, .05, -.12, -.16,
    -.11, -.11, -.23, -.15, -.16, -.15
  )
)

table1 <- bind_rows(ccae, optum_dod, optum_ehr)

table1 %>%
  pivot_wider(
    names_from = database, 
    values_from = c(treatment, comparator, std_difference)
  ) %>% 
  relocate(
    "variable", 
    "treatment_ccae", 
    "comparator_ccae", 
    "std_difference_ccae",
    "treatment_optum-dod",
    "comparator_optum-dod", 
    "std_difference_optum-dod"
) %>%
kbl(
  format = "latex",
  align = "r",
  booktabs = TRUE,
  col.names = c(
    "Variable",
    rep(
      c("Teriparatide", "Bisphosphonates", "Std. diff."),
      3
    )
  )
) %>%
add_header_above(
  c(" " = 1, "CCAE" = 3, "OPTUM-DOD" = 3, "OPTUM-EHR" = 3)
)
```

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
suffix <- "age_50_tr_1_q_25_75"

calibrateRiskStratified <- readRDS(
    file.path(
        here(
          "data/processed",
          paste0(
              paste(
                  "calibrateRiskStratified",
                  suffix,
                  sep = "_"
              ),
              ".rds"
          )
        )
    )
) %>%
    filter(
      stratOutcome == 101,
      estOutcome == 101
    ) %>%
    rename("outcome" = "estOutcome")

metaCalibrateRiskStratified <- readRDS(
    file.path(
      here(
        "data/processed",
        paste0(
            paste(
                "metaCalibrateRiskStratified",
                suffix,
                sep = "_"
            ),
            ".rds"
        )
    )
  )
) %>%
    filter(stratOutcome == 101, estOutcome == 101) %>%
    rename("outcome" = "estOutcome")

riskStratified <- calibrateRiskStratified %>%
    mutate(
        hr = exp(logRr),
        lower    = exp(logLb95Rr),
        upper    = exp(logUb95Rr)
    ) %>%
    select(-contains("Rr")) %>%
    mutate(
        type = "single",
        position = case_when(
            database == "ccae" ~ 5,
            database == "optum_extended_dod" ~ 4,
            database == "optum_ehr" ~ 3
        )
    )

metaRiskStratified <- metaCalibrateRiskStratified %>%
    mutate(
        database = "overall",
        type     = "meta",
        position = 1
    ) %>%
    relocate(database, .after = stratOutcome)

combined <- rbind(riskStratified, metaRiskStratified)

absolute <- readRDS(here("data/processed/mappedOverallAbsoluteResults.rds")) %>%
    filter(
        analysisType == "age_50_tr_1_q_25_75",
        stratOutcome == 101,
        estOutcome   == 101,
        database != "mdcr"
    ) %>%
    mutate(
        estimate = 100 * estimate,
        lower    = 100 * lower,
        upper    = 100 * upper
    )
```

When using the internally developed hip fracture risk prediction
models to divide the population into lower 75\% and top 25\% risk
subgroups, we estimated calibrated hazard ratios of 
`r combined %>% filter(database == "ccae", riskStratum == "Q1") %>% pull(hr)`
(`r combined %>% filter(database == "ccae", riskStratum == "Q1") %>% pull(lower)`
to
`r combined %>% filter(database == "ccae", riskStratum == "Q1") %>% pull(upper)`;
95\% CI),
`r combined %>% filter(database == "optum_extended_dod", riskStratum == "Q1") %>% pull(hr)`
(`r combined %>% filter(database == "optum_extended_dod", riskStratum == "Q1") %>% pull(lower)`
to
`r combined %>% filter(database == "optum_extended_dod", riskStratum == "Q1") %>% pull(upper)`;
95\% CI) and
`r combined %>% filter(database == "optum_ehr", riskStratum == "Q1") %>% pull(hr)`
(`r combined %>% filter(database == "optum_ehr", riskStratum == "Q1") %>% pull(lower)`
to
`r combined %>% filter(database == "optum_ehr", riskStratum == "Q1") %>% pull(upper)`;
95\% CI) in the lower 75\% hip fracture risk subgroup in CCAE,
Optum-DOD and Optum-EHR, respectively. These translated to absolute risk reductions of 
`r absolute %>% filter(riskStratum == "Q1", database == "ccae") %>% pull(estimate)`
(`r absolute %>% filter(riskStratum == "Q1", database == "ccae") %>% pull(lower)`
to
`r absolute %>% filter(riskStratum == "Q1", database == "ccae") %>% pull(upper)`;
95\% CI), 
`r absolute %>% filter(riskStratum == "Q1", database == "optum_extended_dod") %>% pull(estimate)`
(`r absolute %>% filter(riskStratum == "Q1", database == "optum_extended_dod") %>% pull(lower)`
to
`r absolute %>% filter(riskStratum == "Q1", database == "optum_extended_dod") %>% pull(upper)`;
95\% CI) and
`r absolute %>% filter(riskStratum == "Q1", database == "optum_ehr") %>% pull(estimate)`
(`r absolute %>% filter(riskStratum == "Q1", database == "optum_ehr") %>% pull(lower)`
to
`r absolute %>% filter(riskStratum == "Q1", database == "optum_ehr") %>% pull(upper)`;
95\% CI) in CCAE, Optum-DOD and Optum-EHR respectively. Regarding hip
fracture risk, the overall meta-analytic hazard ratio of the effect of
teriparatide compared to oral bisphosphonates in the lower 75\% hip
fracture risk subgroup was
`r combined %>% filter(database == "overall", riskStratum == "Q1") %>% pull(hr)`
(`r combined %>% filter(database == "overall", riskStratum == "Q1") %>% pull(lower)`
to
`r combined %>% filter(database == "overall", riskStratum == "Q1") %>% pull(upper)`;
95\% CI) across all 3 databases in the lower risk subgroup.

In the upper 25\% hip fracture risk subgroup we estimated hazard ratios of
`r combined %>% filter(database == "ccae", riskStratum == "Q2") %>% pull(hr)`
(`r combined %>% filter(database == "ccae", riskStratum == "Q2") %>% pull(lower)`
to
`r combined %>% filter(database == "ccae", riskStratum == "Q2") %>% pull(upper)`;
95\% CI),
`r combined %>% filter(database == "optum_extended_dod", riskStratum == "Q2") %>% pull(hr)`
(`r combined %>% filter(database == "optum_extended_dod", riskStratum == "Q2") %>% pull(lower)`
to
`r combined %>% filter(database == "optum_extended_dod", riskStratum == "Q2") %>% pull(upper)`;
95\% CI) and
`r combined %>% filter(database == "optum_ehr", riskStratum == "Q2") %>% pull(hr)`
(`r combined %>% filter(database == "optum_ehr", riskStratum == "Q2") %>% pull(lower)`
to
`r combined %>% filter(database == "optum_ehr", riskStratum == "Q2") %>% pull(upper)`;
95\% CI) in the lower 75\% hip fracture risk subgroup in CCAE,
Optum-DOD and Optum-EHR, respectively. These translated to absolute risk reductions of 
`r absolute %>% filter(riskStratum == "Q2", database == "ccae") %>% pull(estimate)`
(`r absolute %>% filter(riskStratum == "Q2", database == "ccae") %>% pull(lower)`
to
`r absolute %>% filter(riskStratum == "Q2", database == "ccae") %>% pull(upper)`;
95\% CI), 
`r absolute %>% filter(riskStratum == "Q2", database == "optum_extended_dod") %>% pull(estimate)`
(`r absolute %>% filter(riskStratum == "Q2", database == "optum_extended_dod") %>% pull(lower)`
to
`r absolute %>% filter(riskStratum == "Q2", database == "optum_extended_dod") %>% pull(upper)`;
95\% CI) and
`r absolute %>% filter(riskStratum == "Q2", database == "optum_ehr") %>% pull(estimate)`
(`r absolute %>% filter(riskStratum == "Q2", database == "optum_ehr") %>% pull(lower)`
to
`r absolute %>% filter(riskStratum == "Q2", database == "optum_ehr") %>% pull(upper)`;
95\% CI) in CCAE, Optum-DOD and Optum-EHR respectively. Regarding hip
fracture risk, the overall meta-analytic hazard ratio of the effect of
teriparatide compared to oral bisphosphonates in the lower 75\% hip
fracture risk subgroup was
`r combined %>% filter(database == "overall", riskStratum == "Q2") %>% pull(hr)`
(`r combined %>% filter(database == "overall", riskStratum == "Q2") %>% pull(lower)`
to
`r combined %>% filter(database == "overall", riskStratum == "Q2") %>% pull(upper)`;
95\% CI) across all 3 databases in the upper risk subgroup.
